### 2017-06-21 src/algorithm.tex
fig
fix

\begin{figure}[ht]
\centering
\input{fig-dp1}
\caption[]{
\label{fig:dp1}
The optimal embedding of a $\sigma \gamma $-path into a $sw$ path can be efficiently 
computed by breaking the problem into the problem of embedding a $\sigma \alpha $-path
into a $sv$-path (blue, dashed rectangles) 
and the problem of embedding a $\alpha \gamma $-path into $w$ (red, dotted
rectangles) where $b_d(\alpha , \beta ) \leq b_c(v, w)$.
}
\end{figure}

>>>>

\begin{figure}[ht]
\centering
\input{fig-dp2}
\caption[]{
\label{fig:dp1}
The optimal embedding of a $\sigma \gamma $-path into a $sv$ path can be
efficiently computed by breaking the problem into the problem of embedding 
a $\sigma \alpha $-path into a $su$-path (blue, dashed clouds) 
and the problem of embedding a $\beta \gamma $-path into $v$ (orange, dotted) 
where $b_d(\alpha , \beta) \leq b_c(u, v)$.
}
\end{figure}
